Capitalized Title Here

### 2021-03-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
marked further questions

The automated framework  used in this paper was proposed by @aoas. In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr]. `x3ptools` \hh{is a package to read, write, and generally, process } x3p files. 
<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).--> 
<!--\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper). Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face. Engravings are scratch marks.}-->
\hh{\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.}
\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area. The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
<!--\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description. Could you instead describe things conceptually, and then link to the code that does this particular image?} -->
The white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view. <!--Then we can acquire the crosscut data (`ccdata`) of the scan at this height. --> \hh{XXX passive voice for things that are not part of this paper :)}
Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)). A non-parametric LOESS smooth  [@loess] is fit to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth. 
\hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures. To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny],}   `bulletinspectR` to identify and correct those errors. 
\hh{An example of the extraction process with corresponding code and parameter settings can be found at XXX.}
Note that \hh{the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.}

@@

### Conceptual idea of CMPS
\hh{Most algorithms for comparing striation marks are based on the digitized signatures XXX and produce a similarity score (some citations: chumbley score, Ganesh's fix, vorburger's ccf paper, hare).} 
 The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm. The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference profile  and  for each segment find the "best" registration position on the comparison profile (the other bullet signature) with respect to their cross-correlation values. \hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score. 
\hh{High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.} 
\hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
 The CMPS algorithm can assist firearm examiners with drawing a conclusion \hh{about the source of a comparison pair}. \hh{Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the } CMPS algorithm. 
Thus, in this paper we present an open-source implementation of the CMPS algorithm \hh{in the R package CMPS available from XXX github / CRAN}. 
With our implementation, one can compute the CMPS score of a comparison using the following code:

@@

\hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}

@@

1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
the command `get_segs(x, len=50)` implements this first step. 
It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.

@@

>>>>

The automated framework  used in this paper was proposed by @aoas. In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr]. `x3ptools` \hh{is a package to read, write, and generally, process } x3p files. 
<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).--> 
<!--\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper). Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face. Engravings are scratch marks.}-->
\hh{\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.}
\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area. The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
<!--\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description. Could you instead describe things conceptually, and then link to the code that does this particular image?} -->
The white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view. <!--Then we can acquire the crosscut data (`ccdata`) of the scan at this height. --> \hh{XXX passive voice for things that are not part of this paper :)}
Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)). A non-parametric LOESS smooth  [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth. 
\hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures. To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny],}   `bulletinspectR` to identify and correct those errors. 
\hh{An example of the extraction process with corresponding code and parameter settings can be found at XXX.}
Note that \hh{the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.}

@@

### Conceptual idea of CMPS
\hh{Most algorithms for comparing striation marks are based on the digitized signatures XXX and produce a similarity score (some citations: chumbley score, Ganesh's fix, vorburger's ccf paper, hare).} 
 The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm. The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference profile  and  for each segment find the "best" registration position on the comparison profile (the other bullet signature) with respect to their cross-correlation values. \hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score. 
\hh{High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.} 
\hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
\wj{they didn't talk about a specific threshold or error rates}
 The CMPS algorithm can assist firearm examiners with drawing a conclusion \hh{about the source of a comparison pair}. \hh{Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the } CMPS algorithm. 
Thus, in this paper we present an open-source implementation of the CMPS algorithm \hh{in the R package CMPS available from XXX github / CRAN}. 
With our implementation, one can compute the CMPS score of a comparison using the following code:

@@

\hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}
\wj{further question?}

@@

1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
the command `get_segs(x, len=50)` implements this first step. 
It takes a profile \hh{XXX profile or signature?} \wj{further question?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.

@@

<!-- open source -->
<!-- module -->
<!-- hamby 44 new data set -->
<!-- hamby 252 -->
<!-- threshold -->
